Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-06-06 src/docs_bioinference-poster/bioinference-poster.Rmd
Finish BioInference poster #36

```{r fig4, echo=FALSE, fig.align='center', fig.cap='TMB is biased at estimating second 90 exceedance probabilities for women.'}
knitr::include_graphics("fig4.png")
```

@@

* `r fontawesome::fa("home", fill = "black")` `athowes.github.io`
* `r fontawesome::fa("envelope", fill = "black")` `ath19@ic.ac.uk`
* `r fontawesome::fa("twitter", fill = "black")` `@adamhowes`

@@

<!-- To-do: -->
<!-- * Add sex legend to Fig 4 -->
<!-- * Get "3. Inference procedure" to be on next page -->
<!-- * Try to reduce whitespace around Fig 3 -->

>>>>

```{r fig4, echo=FALSE, fig.align='center', fig.cap='Both approximate methods are meaningfully incorrect for policy.'}
knitr::include_graphics("fig4.png")
```

@@

**Contact** `r fontawesome::fa("home", fill = "black")` `athowes.github.io`; `r fontawesome::fa("envelope", fill = "black")` `ath19@ic.ac.uk`

@@

<!-- To-do: -->
<!-- * Get "3. Inference procedure" to be on next page -->
<!-- * Try to reduce whitespace around Fig 3 -->
